Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-04-27 paper/ref/20160427_referee_response_01.txt

Dear Editor Bertout,

I have read and given considerable thought to the comments and questions posed by the reviewer. Much time has passed since the reviewer submitted the review, a fact that reflects the attention I gave to their comments and how much their comments influenced the further development of the magnetic models. Their emphasis that the intermediate mass star population was of importance was accurate, so I felt it wise to devote significant time and energy to ensuring that this region was well modeled. I believe I achieved this aim. Ultimately, I am very grateful for their excellent review.

The reviewers reading of the manuscript and comments concerning model convergence issues prompted a more extensive study regarding the effects of magnetic fields on the properties of the intermediate mass star population. During this study, I was able to uncover the source of the model's convergence issues, allowing a larger grid of magnetic stellar evolution models to be computed. This led to some interesting results. In particular, a significant amount of time was devoted to addressing disagreements between the morphology of the HR diagram in the region where surface convective envelopes are disappearing. This more extensive investigation led to significant revisions of the discussion section to address potential physical explanations for the observed disagreements and also physical explanation for notable attributes that are in agreement (convergence of magnetic model isochrones with standard model isochrones).

All changes made to the manuscript are marked with bold text and are summarized below.

Sincerely,

Gregory Feiden

----

Summary of key changes:

- The abstract was revised for clarity and two sentences were added to reflect results from the extension of models to the intermediate mass regime.

- A paragraph in the introduction mentioning lithium depletion was removed as it wasn't necessary for providing background to the problem.

- References to David et al. (2016) were added, including a couple sentence at the end of Section 3. This work appeared after initial submission, but contains data on the same eclipsing binary that was analyzed by Kraus et al. (2015).

- Changes to the stellar evolution made to mitigate convergence issues are discussed in Section 2.

- A log(g) column was added to Table 1.

- All figures were updated to include new models and to improve clarity.

- Section 4.2 now discusses the transition region in the HR diagram that arose from my extension of the magnetic models to higher masses.

- Section 5 includes more extensive discussion of B-type stars.

- Section 5.1 was added to discuss the physics underlying the transition region observed in the HR diagram.

- Section 5.2 was created from the end of the old Section 5.1.

- Section 5.3 is presented without discussion of model convergence issues and mentions carbon/nitrogen abundances, which also play a key role in governing the brief period of radius inflation.

- I've tried to clarify the discussion of starspots vs magnetic inhibition of convection.

- More references were added to the discussion of the lithium depletion boundary.

- The summary and conclusions section was expanded.

====

I would like thank the reviewer for a careful reading of the manuscript and their astute analysis of the convergence problems. Their comments and questions motivated a more detailed study of numerical convergence for the intermediate mass star population; a study that temporarily mitigated the original problem. This resulted in an interesting comparison of the intermediate mass star population in the region of the HR diagram where surface convection zones are expected to disappear. There may be very interesting physics occurring in this region that warrant further study. Section 5 has been extended to address interesting points that arose from this investigation.

>> 1. In the introduction and in the discussion of Li depletion, it is worthwhile to mention the recent paper on the same subject by MacDonald & Mullen (2015, MNRAS, 448, 2019).

Mention of lithium depletion in the introduction has been removed since it was not the primary focus of the paper. However, we did reference MacDonald & Mullan (2015) in the discussion of lithium depletion.

>> 2. **I appreciate that the following may be difficult to accomplish given the current state of the field, so I only ask the author to comment on the following, and discuss possible directions for future study.** The equipartition argument derives the surface gas pressure from atmosphere models that neglect magnetic fields. Whereas a self-consistent treatment would be more appropriate. What is required in order for the atmosphere and interior to be treated on equal footing w.r.t. magnetic field?

It's very true that it's difficult to address this problem given the current state of the field, although there is an effort being made to relieve this uncertainty.

To treat the atmosphere and interior on equal footing with respect to the magnetic field, one must either compute a new grid of atmosphere models with magnetic fields or one must incorporate detailed frequency-dependent radiative transfer in stellar evolution models. The former is intractable, as it would require a number of new atmosphere grids that are calculated with different magnetic field strengths.

It's my opinion that the second option is more viable, although difficult in practice. Incorporating detailed radiative transfer in stellar evolution calculations effectively requires model atmospheres to be computed simultaneously with stellar interior models. This is computationally expensive, but feasible. The difficulty is related to the best way of incorporating the magnetic field, such as how the magnetic field interacts with the plasma in the stellar atmosphere. Nevertheless, if this can be achieved, then it will be possible to calculate accurate surface boundary conditions on the fly including effects due to magnetic fields.

>> 3. In Section 3 we see (Figure 1) that the magnetic isochrone does not extend to such high masses as the standard models. We have to wait until Section 5 to learn why. It would be useful to the reader to have this information up front.

Agreed, information about model limitations should be presented earlier. They are now discussed in Section 2, although in a revised context since we were able to mitigate issues that prevented models from extending to higher masses (see point 5 below).

>> 4. I also note that the different panels of Figure 1 are not labelled although they are referred to as a,b,c in the caption and text.

Panels in Figure 1 are now labeled properly.

>> 5. The issue of what happens to higher mass stars than are modelled with magnetic fields in this paper is extremely important and I would encourage the author to discuss briefly what the issues with convergence are.  This will help the reader to understand the problem and may also help others who wish to work on magnetic models in the future as to what problems they may expect to encounter.  As I read it, it seems that the problem with surface magnetic fields occurs just as we would expect the surface convection zone to disappear above 1 Msol.

An astute analysis by the reviewer. I'll first note that the issue was largely mitigated. The problems and temporary solutions are discussed in Section 2.

The principle problem was, as the reviewer noted, the disappearance of the surface convection zone. Models presented by Feiden & Chaboyer (2013) linearly scaled the width of the Gaussian perturbation with the size of the surface convection zone. This prevented models of lower mass stars from having absurdly strong magnetic fields and allowed the magnetic field to vary more slowly throughout their deep surface convection zones. Model for solar-like stars, however, had a more localized (strongly peaked) magnetic field.

Issues with numerical convergence in the first version of the paper was a consequence of the Gaussian width going to zero, causing enormous magnetic field strengths near the tachocline, which was already situated close the stellar surface. The strong radial magnetic field strength gradient prevented the models from converging. By temporarily fixing the minimum value for the Gaussian width, I've avoided these numerical issues. The precise minimum value had little to no impact on the final results.

>> 6. To quote the estimated age of the system as 9-10 Myr, rather than 9.5 /-0.5 Myr, is perhaps more appropriate to the way the age is treated in the paper. We only see models with ages 5, 10, 15 Myr and no statistical analysis is done.

This is a fair point. The estimated median age is now quoted as 9 - 10 Myr.

>> 7. The stars above which no magnetic models are available are very close to the regime where they will arrive on the main sequence (as noted in the text to begin H-burning in the core), and since such models should have no surface convection zones on the main sequence (M > 1.3 Msol), we might benefit from a more detail about why the models fail to converge. This is certainly of interest to modellers who may try to conduct similar studies.

Agreed, but as mentioned in point 5, this problem has been temporarily relieved.

>> 8. The discussion of magnetic inhibited convection vs. star spots in curious to me because I would expect that they are each a manifestation of the same underlying phenomenon, i.e., magnetic fields in the outer layers of these stars. In this sense I find that the way the two are presented as distinct effects difficult. This also get back to point #2 above in which it would be very interesting to know whether both can be included in the same models.

Yes, this is an overly nuanced discussion. The reviewer is quite correct that starspots are the manifestation of magnetic inhibition of convection. They're discussed separately in Section 5 to highlight that theoretical formulations treat them as distinct phenomena. Magnetic inhibition of convection, in a stellar model sense, has only been treated as a global phenomenon (Mullan & MacDonald; Lydon & Sofia; Feiden & Chaboyer), where as starspots explicitly account for the level of surface coverage (Chabrier et al.; Jackson & Jeffries; Somers & Pinsonneault).

One might naively assume that magnetic inhibition of convection would produce more exaggerated results, since it's a global prescription. However, if magnetic inhibition of convection can reproduce the properties of stars with realistic magnetic field strengths, it suggests that the global description of the magnetic field is not a horrible assumption. Starspots models may then require high surface coverages (approaching 100%) in order to mimic the global prescription of models with magnetic inhibition of convection.

I've tried to make this more clear in Section 5.4.

>> 9. Can the author produce an age estimate from the decay of apsidal motion in HD 144548? If so, how does it compare with the other estimates?

In short, yes, but not reliably. An initial age estimate yielded an age around 15 - 20 Myr. While this is encouraging, it should be approached with caution.

The principle difficulty in deriving an age from the apsidal motion rate for HD 144548 is that the "secondary star" in the system is itself a binary. This poses problems when considering the age dating method proposed by Feiden & Dotter (2013). Namely, defining a suitable average interior structure constant (k2) for the inner binary that adequately describes the resulting gravitational potential, and defining a single "radius" for the inner binary.

>> 10. Finally, I note one reference that may be of interest on the subject of core magnetic fields from Kepler/K2, Fuller et al. 2015 (Science, 350, 423)

Yes, the paper by Fuller et al. on suppression of gravity waves in the cores of red giants is very interesting and quite relevant in terms of providing observational support for dynamo-generated magnetic fields in the cores of intermediate mass stars. The Fuller paper and two subsequent papers by the same group are now cited to motivate future inclusion of magnetic inhibition of convection in core convection descriptions.

### 2016-04-27 paper/ms.tex
Resubmitted version

   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: February DD, 2016.}

@@

While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle. Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties. However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2015b, Lodieu2015}. This opens up new territory for assessing hypotheses as to the origin of the noted age discordance. Models can now be constrained in the HR diagram with added constraints from the eclipsing binary mass-radius relationship. The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}. Compare this to conversions from spectral types and photometric colors to \teff s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}. Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.

\citet{Kraus2015} examined stellar model agreement using the properties of a low-mass eclipsing binary, UScoCTIO5, that has two roughly 0.3 \msun\ stars with precisely measured radii. What they found was that \object{UScoCTIO5} has an estimated age of about 5 Myr if inferred from the HR diagram, consistent with the age of other low-mass stars in Upper Scorpius \citep{Preibisch2002, Slesnick2008}. Surprisingly, the age inferred for UScoCTIO5 from the mass-radius relationship implies UScoCTIO5 is about 8 Myr old, more in line with \citet{Pecaut2012}. {\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2015b}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}. Stellar ages are not only dependent on the effective temperature of stars used in the analysis, but on the specific properties adopted. It appears that stellar evolution models are unable to provide consistent ages on multiple levels.

@@

In addition to the photometric samples, properties of two eclipsing multiple-star systems recently observed by \emph{Kepler}/K2 are included. The first of these systems, UScoCTIO5, is a low-mass eclipsing binary (\porb$= 34$ days) with a $M_A = 0.329\pm0.002$\msun\ primary and a $M_B = 0.317\pm0.002$\msun\ secondary \citep{Kraus2015}. Radii were also measured and found to be $R_A = 0.834\pm0.006$\rsun\ and $R_B = 0.810\pm0.006$\rsun\ for the primary and secondary, respectively. Extracting reliable effective temperatures for components of eclipsing binary systems is notoriously difficult. However, the similarity between the two stars in UScoCTIO5 ($F_B/F_A \approx T_B/T_A \approx 1$) allows \citet{Kraus2015} to apply several different techniques for determining component effective temperatures, including directly determining the total system bolometric flux [\fbol$= (2.02\pm0.10)\times10^{-10}\textrm{ erg s}^{-1}$]. Assuming a distance of $145\pm15$~pc \citep{deZeeuw1999}, they estimate that $T_{{\rm eff}, A, B} = 3200\pm75$~K. {\bf Properties determined by \citet{David2015b} will be discussed in Sect.~\ref{sec:results}.}

@@

{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2015b, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level. Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems. {\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

Moreover, inspection of the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems. It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses compared to at lower masses. This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations. Although agreement is good, it is not perfect. {\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2015b}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2015b}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively. An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.

@@

{\bf In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$. Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a). The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are beginning to enter a brief period of radius inflation that accompanies the ignition of CN-cycle burning \citep{Iben1965}. Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths. As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$. Stars above 1.40 $M_{\odot}$ then become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}

@@

{\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition. Another mechanism must be responsible and the failure of magnetic models to reproduce the sharp transition suggests the mechanism is not accounted for in the models.}

{\bf The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology. Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass. Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 \star$. It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}

@@

{\bf There are several implications of this result. First, the sudden knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology. Second, the shift in magnetic field topology from predominantly axisymmetric to non-axisymmetric may when the radiative core mass is much larger than initially suggested, $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$, respectively. Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}

{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true. That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies. The shift in magnetic field topology may affect magnetic wind breaking mechanisms causing stars to exhibit anomalous rotation periods at older ages \citep{vanSaders2016}. This hypothesis may be at odds with the dependence of magnetic wind breaking mechanisms on large-scale magnetic field topologies, which suggest dipolar magnetic fields exert a greater torque on a star than multi-polar fields \citep[e.g.,][]{Reville2015}. However, it is unclear how the transition from a non-axisymmetric to axisymmetric magnetic field topologies affects this picture.}

{\bf This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram. The shallower slope may be an artifact of how the empirical locus was computed. The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars. However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected. While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend of should be robust against errors in how the empirical locus is computed.}

@@

{\bf The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects. This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off, perhaps because magnetic models do not account for shifts in global magnetic field topology.}
If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $5\,000 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of convection zone depth and convective core size.

@@

Presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}. Not only will magnetic inhibition of convection shift mass estimates for cool stars toward higher masses, but a gradually declining magnetic field in the regime of 1.4 \msun\ should result in a paucity of stars in the 4500~K -- 5500~K temperature range. Standard stellar initial mass functions \citep[e.g.,][]{Salpeter1955, Kroupa2002} predict a certain number of stars at a given mass relative to other masses. Having a range of magnetic field strengths in stars over such a narrow mass range (0.16 \msun) will spread stars of similar mass across a wider range in temperature. It's not clear from \citet{Preibisch2002} whether this paucity is observed. However, they do note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002} that appears consistent with predictions from magnetic models. The impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.

@@

\subsection{Radius of HD 144548 A}
\label{sec:radius}
Figure~\ref{fig:mrd} reveals that the radius of HD 144548 A is significantly larger than is expected from standard stellar evolutionary predictions. This poses a problem to claims of consistent ages across stellar populations in Upper Scorpius. However, it is not immediately clear that the observed radius error is a true astrophysical problem. For instance, adopting the effective temperature and luminosity estimate from \citet{Pecaut2012}, one derives a radius of $R = 2.2 \pm 0.2 R_{\odot}$. This is formally consistent with the radius derived by \citep{Alonso2015}, but the mean value is more consistent with estimates from stellar evolution isochrones around 10 Myr. Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated {\bf as a function of stellar mass and age} in Fig.\ \ref{fig:bump}. As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from the $p$--$p$ chain and gravitational contraction of the core.

>>>>

   \date{Version: \today; Submitted: October 21, 2015; Re-submitted: April 27, 2016.}

@@

While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle. Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties. However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2016, Lodieu2015}. This opens up new territory for assessing hypotheses as to the origin of the noted age discordance. Models can now be constrained in the HR diagram with added constraints from the eclipsing binary mass-radius relationship. The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}. Compare this to conversions from spectral types and photometric colors to \teff s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}. Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.

\citet{Kraus2015} examined stellar model agreement using the properties of a low-mass eclipsing binary, UScoCTIO5, that has two roughly 0.3 \msun\ stars with precisely measured radii. What they found was that \object{UScoCTIO5} has an estimated age of about 5 Myr if inferred from the HR diagram, consistent with the age of other low-mass stars in Upper Scorpius \citep{Preibisch2002, Slesnick2008}. Surprisingly, the age inferred for UScoCTIO5 from the mass-radius relationship implies UScoCTIO5 is about 8 Myr old, more in line with \citet{Pecaut2012}. {\bf There is some disagreement about the precise values for the masses and radii of UScoCTIO5 \citep{David2016}, but the mass-radius relationship nevertheless suggests an age of 7 -- 8 Myr}. Stellar ages are not only dependent on the effective temperature of stars used in the analysis, but on the specific properties adopted. It appears that stellar evolution models are unable to provide consistent ages on multiple levels.

@@

In addition to the photometric samples, properties of two eclipsing multiple-star systems recently observed by \emph{Kepler}/K2 are included. The first of these systems, UScoCTIO5, is a low-mass eclipsing binary (\porb$= 34$ days) with a $M_A = 0.329\pm0.002$\msun\ primary and a $M_B = 0.317\pm0.002$\msun\ secondary \citep{Kraus2015}. Radii were also measured and found to be $R_A = 0.834\pm0.006$\rsun\ and $R_B = 0.810\pm0.006$\rsun\ for the primary and secondary, respectively. Extracting reliable effective temperatures for components of eclipsing binary systems is notoriously difficult. However, the similarity between the two stars in UScoCTIO5 ($F_B/F_A \approx T_B/T_A \approx 1$) allows \citet{Kraus2015} to apply several different techniques for determining component effective temperatures, including directly determining the total system bolometric flux [\fbol$= (2.02\pm0.10)\times10^{-10}\textrm{ erg s}^{-1}$]. Assuming a distance of $145\pm15$~pc \citep{deZeeuw1999}, they estimate that $T_{{\rm eff}, A, B} = 3200\pm75$~K. {\bf Properties determined by \citet{David2016} will be discussed in Sect.~\ref{sec:results}.}

@@

{\bf Fundamental properties for the eclipsing binary EPIC 203710387 \citep{David2016, Lodieu2015} are not included in the main analysis because the component masses are uncertain at the 0.02 \msun\ level. Discussion with respect to model predictions in light the two fundamental property determinations will be presented in Sect.~\ref{sec:disc}.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems. {\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

Moreover, inspection of the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems. It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses compared to at lower masses. This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations. Although agreement is good, it is not perfect. {\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively. An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.

@@

{\bf In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$. Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a). The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}. Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths. As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$. Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}

@@

{\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition. Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature. However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K. Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.} 
%suggests the mechanism is not accounted for in the models.}

{\bf The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology. Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass. Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$. It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}

@@

{\bf The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested. Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.}

%Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
%{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true. That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies. The shift in magnetic field topology may affect magnetic wind breaking mechanisms causing stars to exhibit anomalous rotation periods at older ages \citep{vanSaders2016}. This hypothesis may be at odds with the dependence of magnetic wind breaking mechanisms on large-scale magnetic field topologies, which suggest dipolar magnetic fields exert a greater torque on a star than multi-polar fields \citep[e.g.,][]{Reville2015}. However, it is unclear how the transition from a non-axisymmetric to axisymmetric magnetic field topologies affects this picture.}

{\bf This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram. The shallower slope may be an artifact of how the empirical locus was computed. The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars. However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected. While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.}

@@

{\bf The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects. This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology.}
If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of {\bf stellar surface convection zone properties.}

@@

\subsection{Initial Mass Function}
The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}. {\bf Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures. As a result, stars with a given effective temperature and luminosity have a higher mass when magnetic inhibition of convection is considered. Furthermore, the presence of a transition region characterized by gradually declining influence of stellar magnetic fields that links the magnetic and non-magnetic sequences will tend spread stars with similar masses across a larger effective temperature domain.

For example, consider the predicted mass difference between a star with $T_{\rm eff} = $ 6\,000~K and one with $T_{\rm eff} = $ 4\,500~K. Non-magnetic models predict a mass difference of 0.85 \msun\ and 0.50 \msun\ at 5 Myr and 10 Myr, respectively. However, magnetic models suggest that the mass difference is 0.25 \msun\ at 10 Myr. This is at least a factor of two smaller than standard model predictions.

Neglecting magnetic inhibition of convection would produce stellar mass distributions that show a paucity of stars at higher masses compared to standard predictions for field and cluster initial mass function \citep[e.g.,][]{Salpeter1955, Kroupa2002, Chabrier2003}. \citet{Preibisch2002} note a possible excess of low-mass stars compared to field initial mass functions \citep{Scalo1998, Kroupa2002}, but it's not immediately clear whether this potential excess of low-mass stars is fully consistent with predictions from magnetic model predictions. Assessing the impact of magnetic inhibition of convection on the (sub)stellar initial mass function of Upper Scorpius is reserved for future work.}

@@

\subsection{Radius of HD 144548 A}
\label{sec:radius}
Figure~\ref{fig:mrd} reveals that the radius of HD 144548 A is significantly larger than is expected from standard stellar evolutionary predictions. This poses a problem to claims of consistent ages across stellar populations in Upper Scorpius. However, it is not immediately clear that the observed radius error is a true astrophysical problem. For instance, adopting the effective temperature and luminosity estimate from \citet{Pecaut2012}, one derives a radius of $R = 2.2 \pm 0.2 R_{\odot}$. This is formally consistent with the radius derived by \citep{Alonso2015}, but the mean value is more consistent with estimates from stellar evolution isochrones around 10 Myr. Stellar models show an increase in stellar radius for stars with masses in the vicinity of $M = 1.5$\msun, illustrated {\bf as a function of stellar mass and age} in Fig.\ \ref{fig:bump}. As described in {\bf Sect.\ \ref{sec:dynamo}}, this radius increase is due to the convective envelope responding to increased energy generation from CN cycle ignition.
